Interpretable Machine Learning

### 2017-12-04 talk.Rmd
update link
add kaggle obd license disclaimer

@@

Read my book about "Interpretable Machine Learning"
https://christophm.github.io/xai-book/

>>>>

<font size="2">Contains information from Kaggle ML and Data Science Survey, 2017, which is made available here under the Open Database License (ODbL).</font>

@@

Read my book about "Interpretable Machine Learning"
https://christophm.github.io/interpretable-ml-book/
